Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-05-18 paper/paper.tex
Additional infos for RTPJ and synaptic epigenesis

\begin{equation}
  \pi^{\text{hard-max}}(s) = \argmax_{a \in \mathcal A}\tilde{Q}(s, a|\theta),
  \label{eq:policy}
\end{equation}
This defines a mapping from states directly to actions.
% $a \mapsto \tilde{Q}(a,s|\theta)$ of the $Q$-value function ``frozen'' at state $s$.
For instance, a simple linear model with a kernel $\phi$ would be of the
form $\tilde{Q}(s, a|\theta) = \phi(s,a)^T\theta$, where
$\phi(s,a)$ would represent a high-level representation of the state-action pairs
$(s,a)$, as was done proposed \citep{songNIPS2016}, or a eural network as recently proposed by in the
breakthrough works
\citep{mnih2015,silver2016mastering} for playing complex games (atari, Go, etc.) at superhuman levels.
%  and Parr et al. 2003 (JMLR)].
In the DMN, the dmPFC would implement such a hard-max lookup
over the action space.
The model
  parameters $\theta$ would correspond to synaptic weights and connection strengths between
  brain regions. It is a time-varying neuronal program which dictates how to move from world states $s$ to actions $a$ via the hard-max policy \eqref{eq:policy}.
  The approximating $Q$-value function $\tilde{Q}(s, a|\theta)$ would tell the DMN the (expected) usefulness of taking an action $a$ in state $s$.
  The DMN, and in particular its dmPFC node, could then contribute to the choice, at a given state $s$, of an action $a$ which maximizes these approximate
  $Q$-values. Such a mapping from states to actions is conventionally called \textit{policy matrix}\citep{mnih2015,silver2016mastering}.
  Learning consists in starting from a given table and
  updating it during action choices,
  which take the agent to different table entries. \suggestadd{An additional layer of learning concerns the addition of new entries in the table (i.e. state and action). The framing of the policy matrix is not described here but could be supported by the formation of new attractor in the neural dynamics through synaptic epigenesis \citep{gisiger_acquisition_2005}.}

@@

\suggestadd{The principal connectivity gradient in the cortex appears to be greatly expanded in humans compare to macaques, suggesting a phylogenetically conserved axis of cortical expansion with the DMN emerging at the extreme-end in humans \citep{margulies_situating_2016}. Neurocomputational models of dyadic whole brain demonstrated how the human connectivity topology, on top of facilitating processing at the intra-individual level, can explain our propensity to coordinate through sensorimotor loops with others at the inter-individual level \citep{dumas_anatomical_2012}.}

>>>>

\begin{equation}
  \pi^{\text{hard-max}}(s) = \argmax_{a \in \mathcal A}\tilde{Q}(s, a|\theta),
  \label{eq:policy}
\end{equation}
This defines a mapping from states directly to actions.
% $a \mapsto \tilde{Q}(a,s|\theta)$ of the $Q$-value function ``frozen'' at state $s$.
For instance, a simple linear model with a kernel $\phi$ would be of the
form $\tilde{Q}(s, a|\theta) = \phi(s,a)^T\theta$, where
$\phi(s,a)$ would represent a high-level representation of the state-action pairs
$(s,a)$, as was done proposed \citep{songNIPS2016}, or a eural network as recently proposed by in the
breakthrough works
\citep{mnih2015,silver2016mastering} for playing complex games (atari, Go, etc.) at superhuman levels.
%  and Parr et al. 2003 (JMLR)].
In the DMN, the dmPFC would implement such a hard-max lookup
over the action space.
The model
  parameters $\theta$ would correspond to synaptic weights and connection strengths between
  brain regions. It is a time-varying neuronal program which dictates how to move from world states $s$ to actions $a$ via the hard-max policy \eqref{eq:policy}.
  The approximating $Q$-value function $\tilde{Q}(s, a|\theta)$ would tell the DMN the (expected) usefulness of taking an action $a$ in state $s$.
  The DMN, and in particular its dmPFC node, could then contribute to the choice, at a given state $s$, of an action $a$ which maximizes these approximate
  $Q$-values. Such a mapping from states to actions is conventionally called \textit{policy matrix}\citep{mnih2015,silver2016mastering}.
  Learning consists in starting from a given table and
  updating it during action choices,
  which take the agent to different table entries. \suggestadd{An additional layer of learning concerns the addition of new entries in the table (i.e. state and action). The framing of the policy matrix is not described here but could be supported by synaptic epigenesis \citep{gisiger_acquisition_2005}. Indeed, the tuning of synaptic weights through learning can stabilize additional patterns of activity by
creating new attractors in the neural dynamics landscape \citep{takeuchi_synaptic_2014}. Those attractors will then constrain both
the number of factors taken into account by decision processes and the number of behaviors at reach by the agent \citep{wang_decision_2008}.}

@@

\suggestadd{The principal connectivity gradient in the cortex appears to be greatly expanded in humans compare to macaques, suggesting a phylogenetically conserved axis of cortical expansion with the DMN emerging at the extreme-end in humans \citep{margulies_situating_2016}. Neurocomputational models of dyadic whole brain demonstrated how the human connectivity topology, on top of facilitating processing at the intra-individual level, can explain our propensity to coordinate through sensorimotor loops with others at the inter-individual level \citep{dumas_anatomical_2012}. DMN is moreover largely overlapping with neural networks associated with higher level social cognition \citep{schilbach_introspective_2012}. For instance, the ventromedial prefrontal cortex, the posterior cingulate/precuneus, and the temporo-parietal junction (rTPJ) play together a key role in bridging the gap between self and other by
integrating low-level embodied processes within higher level inference-based mentalizing \citep{lombardo_shared_2009}.}
